Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-05-16 tex/paper1/paper1.tex
edits to the paper

Coronal seismology is the study of oscillatory phenomena in the solar
corona.  First suggested by \cite{1970PASJ...22..341U}, the practice
of coronal seismology attempts to locate oscillatory phenomena in the
solar corona, identify the wave modes present, and then use
theoretical descriptions of those wave modes to infer the physical
conditions of the solar corona.  The practice of coronal seismology
began in earnest with observations of wave modes by SOHO-EIT \citep{}
and TRACE \citep{} (see also \cite{} for more extensive reviews of
coronal seismology).  Since then, many papers have been published
describing oscillatory phenomena in the corona and their
interpretation in terms of theoretically known wave modes.

@@

>>>>

Coronal seismology is the study of oscillatory phenomena in the solar
corona.  First suggested by \cite{1970PASJ...22..341U}, the practice
of coronal seismology attempts to locate oscillatory phenomena in the
solar corona, identify the wave modes present, and then use
theoretical descriptions of those wave modes to infer the physical
conditions of the solar corona.  The practice of coronal seismology
began in earnest with observations of wave modes by SOHO-EIT
\citep{1998ApJ...501L.217D, 1999SoPh..186..207B} and TRACE
\citep{1999ApJ...520..880A} (see also \cite{} for more extensive
reviews of coronal seismology).  Since then, many papers have been
published describing oscillatory phenomena in the corona and their
interpretation in terms of theoretically known wave modes.

@@

Their relative scarcity has prompted efforts to create automated
oscillation detection algorithms.
